### 2018-10-16 manuscript.rmd
updated plot with new data

papers = read_tsv( "tables/papers.tsv" )
datasets = read_tsv( "tables/datasets.tsv" )
analyses = 
	read_tsv( "tables/analyses.tsv", col_types = 'icccccccccclnnnnccc' ) %>%
	mutate( taxon_sampling = factor( taxon_sampling, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

@@

>>>>

papers = read_tsv( "tables/papers.tsv" )
datasets = read_tsv( "tables/datasets.tsv" )
analyses = 
	read_tsv( "tables/analyses.tsv", col_types = 'iccccccccccclnnnncc' ) %>%
	mutate( taxon_sampling = factor( taxon_sampling, levels= c( 'Choanimalia', 'Holozoa', 'Opisthokonta' ) ) )

@@

A total of `r nrow(analyses)` analyses were transcribed from the literature.
